Bayesian Networks for Assessing Environmental Sustainability in Australian Vineyards

### 2024-06-18 article.tex
lexi table and fig

@@

% \usepackage{booktabs}
\begin{table}[h]\ref{table:definitions}

@@

The key factors identified were defined as shown in Table 1. By utilising these definitions, each factor's contribution to environmental sustainability was assessed. The definitions provided a clear framework for measurement, ensuring that the factors could be consistently evaluated.

@@

>>>>

% Packages:

\usepackage{graphicx}

@@

% \usepackage{booktabs} TODO: check the BN definitions align properly.
\begin{table}[h]\label{tab:definitions} 

@@

The key factors identified were defined as shown in Table \ref{tab:definitions}. By utilising these definitions, each factor's contribution to environmental sustainability was assessed. The definitions provided a clear framework for measurement, ensuring that the factors could be consistently evaluated.

@@

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table}[h]\label{tab:lexi}
    \begin{tabular}{@{}llrr@{}}
    \toprule
    \textbf{Concept} & \textbf{Kind} & \multicolumn{1}{l}{\textbf{Count}} & \multicolumn{1}{l}{\textbf{Relevance_percentage}} \\ \midrule
    water & WORD & 1321 & 100 \\
    change & WORD & 817 & 62 \\
    climate & WORD & 789 & 60 \\
    disease & WORD & 646 & 49 \\
    change & WORD & 569 & 43 \\
    grapevine & WORD & 565 & 43 \\
    viticulture & WORD & 565 & 43 \\
    soil & WORD & 450 & 34 \\
    plant & WORD & 425 & 32 \\
    different & WORD & 300 & 23 \\ \bottomrule
    \end{tabular}
    \end{table}

    \begin{figure}[h]
        \centering
        \includegraphics[width=\linewidth]{Winegrowing-concept-map}
        \caption{Your caption here}
        \label{fig:lexi}
    \end{figure}
